---
title: "3_data_extra_Reynolds_lab"
author: "Bruno S. Carturan, Eric Hertz, Stephanie J. Peacock"
# date: "2025-08-22"
output: 
  html_document:
    toc: true                  # Adds a table of contents to the document
    toc_float: true           # Makes the table of contents float on the side as the reader scrolls.
    toc_collapsed: true        # Starts the table of contents in a collapsed state.
    toc_depth: 3               # Specifies the depth of headers (e.g., ##, ###) to include in the table of contents.
    number_sections: true      # 
    theme: journal  # lumen
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(warning = FALSE, message = FALSE) 
```

```{r, include=FALSE}

# 
rm(list = ls())
graphics.off()

# reset the wd to head using the location of the current script
path <- rstudioapi::getActiveDocumentContext()$path
dirhead <- "population-indicators"
path_ahead <- sub(pattern = paste0("\\",dirhead,".*"),replacement = "", x = path)
wd_head <- paste0(path_ahead,dirhead)
setwd(wd_head)

# Now import functions related to directories.
# Note that the script cannot be called again once the directory is set to the 
# subdirectory of the project (unless setwd() is called again).
source("code/functions_set_wd.R")
source("code/functions_general.R")

# return the name of the directories for the different projects:
subDir_projects <- subDir_projects_fun()

wds_l <- set_working_directories_fun(subDir = subDir_projects$spawner_surveys,
                                     Export_locally = F)
wd_head <- wds_l$wd_head
wd_code <- wds_l$wd_code
wd_data <- wds_l$wd_data
wd_figures <- wds_l$wd_figures
wd_output <- wds_l$wd_output
wd_X_Drive1_PROJECTS <- wds_l$wd_X_Drive1_PROJECTS
wd_pop_indic_data_input_dropbox <- paste(wd_X_Drive1_PROJECTS,
                                         wds_l$wd_population_indicator_data_input_dropbox,
                                         sep = "/")

wd_data_dropbox <- paste(wd_X_Drive1_PROJECTS,
                         wds_l$wd_project_dropbox,
                         "data",sep="/")

wd_references_dropbox <- paste(wd_X_Drive1_PROJECTS,
                               wds_l$wd_project_dropbox,
                               "references",sep="/")

# The datasets to input were outputted by other scripts 
wd_data_input <- wd_output

# Import functions for this specific project
source("Code/functions.R")

library(xlsx)
library(readxl)
library(dplyr)
library(sp) # to calculate distances from geo-spatial coordinates
library(sf)

options(warn = 0)
options(digits = 9) ## 7

export_datasets <- T
```

# Import files

## PSE data

```{r}
#'* Import the cleaned NuSEDS data matched with the cuid and streamid of the PSE *
nuseds_cuid_streamid <- import_mostRecent_file_fun(wd = paste0(wd_output,"/archive"), 
                                                   pattern = "2_nuseds_cuid_streamid")

# head(nuseds_cuid_streamid)

nuseds_cuid_streamid$source_id <- "NuSEDS_20251103"
```

```{r}
#'* Import the NuSEDS field definitions *
nuseds_fields_definitions <- nuseds_fields_definitions_fun(wd_references = wd_references_dropbox)
```

```{r, include=FALSE}
#'* Import the stream - GFE_ID data file from DFO *
#' (emailed from Wu Zhipeng, DFO, 09/04/2024)
#' There are different locations in the 2nd first sheets to we combine them into a unique dataframe
# DFO_All_Streams_Segments <- read_xlsx(paste0(wd_data_dropbox,"/DFO_All_Streams_Segments_20240408.xlsx"),
#                                       sheet = "All Streams")
# 
# DFO_All_Streams_Segments2 <- read_xlsx(paste0(wd_data_dropbox,"/DFO_All_Streams_Segments_20240408.xlsx"),
#                                        sheet = "Stream Segments")
# 
# columns <- c("NME","ID","X_LONGT","Y_LAT")
# DFO_All_Streams_Segments <- rbind(DFO_All_Streams_Segments[,columns],
#                                   DFO_All_Streams_Segments2[,columns]
#                                   # DFO_All_Streams_Segments3[,columns],
#                                   # DFO_All_Streams_Segments4[,columns]
# )
# DFO_All_Streams_Segments <- unique(DFO_All_Streams_Segments)
# 
# rm(DFO_All_Streams_Segments2)
# head(DFO_All_Streams_Segments)
```

```{r, include=FALSE}
#'* Import the conservationunits_decoder.csv *
# datasetsNames_database <- datasetsNames_database_fun()
# fromDatabase <- update_file_csv <- F
# #' # To obtain the generation length and calculate the the "current spawner abundance".
# conservationunits_decoder <- datasets_database_fun(nameDataSet = "conservationunits_decoder.csv",
#                                                    fromDatabase = fromDatabase,
#                                                    update_file_csv = update_file_csv,
#                                                    wd = wd_pop_indic_data_input_dropbox)
```

```{r}
#'* Import the shape files for the Region boundaries *
#' Note that se_boundary/se_boundary.shp is used in 0_assign-regions.R. This is a
#' lighter shape file but contains the same regions. The code here works with 
#' se_boundary.shp.
# regions_shp <- st_read(paste0(wd_pop_indic_data_gis_dropbox,"/se_boundary_regions/se_boundary_regions.shp")) %>%
#   st_transform(crs = 4269)
# unique(regions_shp$regionname)
wd_geo_regions <- gsub("1_PROJECTS","5_DATA/Mapping/study areas/shapefiles/PSE_regions/",wd_X_Drive1_PROJECTS)

regions_shp <- st_read(paste0(wd_geo_regions,"se_boundary_regions_simple/se_boundary_regions_simple.shp")) %>%
  st_transform(crs = 4269)
# unique(regions_shp$Region)

sf_use_s2(FALSE) # so that st_intersects() and st_simplify() can be used
```

```{r}
#'* Import the geodatabase for the CU boundaries  *
wd_geo_cus <- gsub("1_PROJECTS","5_DATA/CUs_Master/GDB/",wd_X_Drive1_PROJECTS)

CUs_gdb <- st_read(paste0(wd_geo_cus,"PSF_CUs_Master.gdb")) %>%
  st_transform(crs = 4269)

# remove non-used region values
cond <- ! CUs_gdb$region_name %in% c("Not Assessed","Arctic/Mackenzie")
CUs_gdb <- CUs_gdb[cond,]
CUs_gdb <- st_simplify(x = CUs_gdb, dTolerance = .002) # to reduce computation time
```

## SFU data

```{r}
#'* Import the SFU data: escapement *
SFU_escap <- read_excel(paste(wd_data_dropbox,"SFU_Escapement_data_Master_PSF.xlsx",sep="/"), 
                       sheet = "Estimates") |>
  as.data.frame()

head(SFU_escap)
# nrow(SFU_escap) # 3853

SFU_escap$source_id <- "Reynolds_20260209"

```

```{r}
#'* Import the SFU data: stream info *
#' Preious file: SFU_Escapement_PSF.xlsx
SFU_stream <- read_excel(paste(wd_data_dropbox,"SFU_Escapement_data_Master_PSF.xlsx",sep="/"), 
                        sheet = "Coordinates") |>
  as.data.frame()

head(SFU_stream)
```

Some checks and modifications:

```{r}
# Remove rows with NAs
cond <- is.na(SFU_escap$estimate.number) | SFU_escap$estimate.number == "NA"
SFU_escap <- SFU_escap[!cond,]
sum(cond) # 1428

# CHECK of duplicated rows --> should all be false
any(duplicated(SFU_escap))
any(duplicated(SFU_escap[,c("reynolds.me","year","species","estimate.number")]))

# CHECK that the stream names match between the two datasets
all(SFU_escap$reynolds.me %in% SFU_stream$SFU_Stream_Name)
all(SFU_stream$SFU_Stream_Name %in% SFU_escap$reynolds.me)
cond <- ! SFU_escap$reynolds.me %in% SFU_stream$`SFU Stream Name`
SFU_escap$reynolds.me [cond] |> unique()

cond <- ! SFU_stream$`SFU Stream Name` %in% SFU_escap$reynolds.me
SFU_stream$`SFU Stream Name`[cond]
# "Fell"

# unique(SFU_stream$SFU_Stream_Name)
# "Beales Left" & "Beales Right" --> "Beales
# "Fell Creek" --> "Fell
#  "Mosquito Bay Left" & "Mosquito Bay Right" --> "Mosquito Bay"

cond <- SFU_escap$reynolds.me == "Fell Creek"
SFU_escap$reynolds.me[cond] <- "Fell"
```

We remove extra data for Beales Left & Right and Mosquito Bay Left and Right because these counts should be combined and the combined counts are also in the data set, as expressed in Arianne Nickels' email: Please note that we split both Mosquito bay and Beales into two streams, so the numbers from "Mosquito bay" are a combination of both "Mosquito bay left" and "Mosquito bay right". This is the same for Beales. The reason is because the streams both share an estuary but then split off once you hit the tree line. DFO considers them one stream, so it might be easiest to stick to that. I thought I'd include the combined data and the split data just in case."

```{r}
cond_remove <- SFU_escap$reynolds.me %in% c("Beales Left","Beales Right",
                                            "Mosquito Bay Left","Mosquito Bay Right")
SFU_escap <- SFU_escap[!cond_remove,]

all(SFU_escap$reynolds.me %in% SFU_stream$`SFU Stream Name`)
all(SFU_stream$`SFU Stream Name` %in% SFU_escap$reynolds.me)
```

## Find ESTIMATE_CLASSIFICATION

```{r}
#' Find for each value in estimate.method the corresponding value in the fields
# https://www.salmonexplorer.ca/methods/analytical-approach.html#data-quality

# correct methods
unique(SFU_escap$estimate.method)
unique(nuseds_cuid_streamid$ESTIMATE_METHOD)
SFU_escap$estimate.method[SFU_escap$estimate.method == "Peak live + Dead"] <- "Peak Live + Dead"

estimate.method_SFU <- unique(SFU_escap$estimate.method)
estimate.method_SFU[! estimate.method_SFU %in% unique(nuseds_cuid_streamid$ESTIMATE_METHOD)]

SFU_escap$ESTIMATE_CLASSIFICATION <- NA
SFU_escap$stream_survey_quality <- NA

cond <- SFU_escap$estimate.method == "Fixed Site Census"
SFU_escap[cond,]
#' For metadata in SFU_Escapement_data_Master_PSF.csv:
#' "Fixed Site Census: Combining one or more raw observations into a single estimate
#' (e.g. add all daily fence observation SIL to create a single annual estimate)."
#' --> Medium-Low: Low to moderate effort (1-4 trips), known survey method --> RELATIVE ABUNDANCE (TYPE-4)
SFU_escap$ESTIMATE_CLASSIFICATION[cond] <- "RELATIVE ABUNDANCE (TYPE-4)"
SFU_escap$stream_survey_quality[cond] <- "Medium-Low"


# for the rest of the values:
methods_SFU_l <- sapply(estimate.method_SFU,function(m){
  cond <- nuseds_cuid_streamid$ESTIMATE_METHOD == m
  if(any(cond)){
    out <- list()
    x <- table(nuseds_cuid_streamid$ESTIMATE_CLASSIFICATION[cond])
    x <- rev(sort(x))
    out[[1]] <- x
    
    x <- table(nuseds_cuid_streamid$stream_survey_quality[cond])
    x <- rev(sort(x))
    out[[2]] <- x
    
    names(out) <- c("ESTIMATE_CLASSIFICATION","stream_survey_quality")
    
  }else{
    out <- NA
  }
  return(out)
})

val <- "Area Under the Curve"
methods_SFU_l[[val]]$ESTIMATE_CLASSIFICATION
methods_SFU_l[[val]]$stream_survey_quality
cond <- SFU_escap$estimate.method == val
SFU_escap$ESTIMATE_CLASSIFICATION[cond] <- "RELATIVE ABUNDANCE (TYPE-4)" # to be conservative
SFU_escap$stream_survey_quality[cond] <- "Medium-Low"

val <- "Expert Opinion"
methods_SFU_l[[val]]$ESTIMATE_CLASSIFICATION
methods_SFU_l[[val]]$stream_survey_quality
cond <- SFU_escap$estimate.method == val
SFU_escap$ESTIMATE_CLASSIFICATION[cond] <- "PRESENCE-ABSENCE (TYPE-6)" 
SFU_escap$stream_survey_quality[cond] <- "Low"

val <- "Peak Live + Dead"
methods_SFU_l[[val]]$ESTIMATE_CLASSIFICATION
methods_SFU_l[[val]]$stream_survey_quality
cond <- SFU_escap$estimate.method == val
SFU_escap$ESTIMATE_CLASSIFICATION[cond] <- "RELATIVE ABUNDANCE (TYPE-4)" 
SFU_escap$stream_survey_quality[cond] <- "Medium-Low"

val <- "Unknown Estimate Method"
methods_SFU_l[[val]]$ESTIMATE_CLASSIFICATION
methods_SFU_l[[val]]$stream_survey_quality
cond <- SFU_escap$estimate.method == val
SFU_escap$ESTIMATE_CLASSIFICATION[cond] <- "UNKNOWN" 
SFU_escap$stream_survey_quality[cond] <- "Unknown"

val <- "Other Estimate Method"
methods_SFU_l[[val]]$ESTIMATE_CLASSIFICATION
methods_SFU_l[[val]]$stream_survey_quality
cond <- SFU_escap$estimate.method == val
SFU_escap$ESTIMATE_CLASSIFICATION[cond] <- "RELATIVE ABUNDANCE (TYPE-4)" 
SFU_escap$stream_survey_quality[cond] <- "Medium-Low"

val <- "Peak Live + Cumulative Dead"
methods_SFU_l[[val]]$ESTIMATE_CLASSIFICATION
methods_SFU_l[[val]]$stream_survey_quality
cond <- SFU_escap$estimate.method == val
SFU_escap$ESTIMATE_CLASSIFICATION[cond] <- "RELATIVE ABUNDANCE (TYPE-4)" 
SFU_escap$stream_survey_quality[cond] <- "Medium-Low"

any(is.na(SFU_escap$ESTIMATE_CLASSIFICATION))

```

# Match locations

There are `r nrow(SFU_stream)` locations to match:

```{r, echo=FALSE}
unique(SFU_stream[,c("SFU Stream Name","Nuseds Names","Latitude_Longitude (River Mouth)")])
```

## Some modifications

Convert coordinates from degrees to decimals:

```{r, echo = F}
# Convert coordinates from degree to decimal
lat_long <- strsplit(x = SFU_stream$`Latitude_Longitude (River Mouth)`,
                     split = " ")

char_toFix <- c("°","'","’","”")
lat_long <- lapply(lat_long,function(ll){
  out <- ll
  for(c in char_toFix){
    out <- gsub(c," ",out)
  }
  out <- gsub("\"W","",out)
  out <- gsub("\"N","",out)
  out <- angle_to_dec_fun(out)
  return(out)
}) 

SFU_stream$Latitude <- sapply(lat_long,function(ll){ll[1]})
SFU_stream$Longitude <- sapply(lat_long,function(ll){ll[2]})
SFU_stream$Longitude <- - SFU_stream$Longitude
```

```{r, echo=FALSE}
unique(SFU_stream[,c("SFU Stream Name","Nuseds Names","Latitude","Longitude")])
```

```{r, include=FALSE}
# remove space in column names in SFU_stream:
colnames(SFU_stream) <- gsub(" ","_",colnames(SFU_stream))

# return the unique locations from nuseds_cuid_streamid 
stream_name_PSE_col <- c("WATERBODY","CENSUS_SITE","sys_nm","AREA","GFE_ID","AREA",
                         "X_LONGT","Y_LAT","region","WATERSHED_CDE")
stream_name_PSE <- unique(nuseds_cuid_streamid[,stream_name_PSE_col])
nrow(stream_name_PSE) # 2540

nuseds_cuid_streamid$AREA |> unique()

unique(SFU_stream$SFU_Stream_Name)
unique(SFU_stream$Nuseds_Names)
```

Add the region field using the PSE's region shape file:

```{r, include=FALSE}
# Add the region field
SFU_stream$region <- NA
for(r in 1:nrow(SFU_stream)){
  # r <- 1
  Latitude <- SFU_stream$Latitude[r]
  Longitude <- SFU_stream$Longitude[r]

  point <- st_as_sf(SFU_stream[r,],coords = c("Longitude","Latitude"), crs = 4269)

  layer_rg <- st_intersects(point, regions_shp)

  if(length(layer_rg[[1]]) == 0){ # no match, try to buffer
    print("Region layer not found - BREAK")
    break
    
  }else if(length(layer_rg[[1]]) > 1){ # no match, try to buffer
    print("More than one region- BREAK")
    break
    
  }else{
    SFU_stream$region[r] <- regions_shp$Region[layer_rg[[1]]]
  }
}
unique(SFU_stream$region)
```

```{r, echo=FALSE}
unique(SFU_stream[,c("region","SFU_Stream_Name","Nuseds_Names","Latitude","Longitude")])
```

## Match locations

We try to match the stream names in **SFU_stream** with those in the PSE.

```{r, include=FALSE}
#' Try to match the stream names in SFU_stream with those in the PSE 
#' (stream_name_PSE). Provide the associated GFE_ID in that case.
SFU_stream$GFE_ID <- NA
SFU_stream$in_PSE <- NA
location_maybe <- data.frame()
for(r in 1:nrow(SFU_stream)){
  # r <- 1
  region <- SFU_stream$region[r]
  SFU_Stream_Name_simple <- simplify_string_fun(SFU_stream$SFU_Stream_Name[r])
  Nuseds_Names <- SFU_stream$Nuseds_Names[r]
  Nuseds_Names_simple <- simplify_string_fun(SFU_stream$Nuseds_Names[r])
  Watershed_Code <- SFU_stream$Watershed_Code[r]
  Area <- as.character(SFU_stream$Area[r])
  
  # r <- which(simplify_string_fun(SFU_stream$SFU_Stream_Name) == "fancyright")
  
  # match found
  if(!is.na(Nuseds_Names)){
    
    cond_NUSEDS <- stream_name_PSE$region == region & 
      (stream_name_PSE$WATERBODY == Nuseds_Names |
         stream_name_PSE$CENSUS_SITE == Nuseds_Names |
         stream_name_PSE$sys_nm == Nuseds_Names) |
      grepl(Watershed_Code,stream_name_PSE$WATERSHED_CDE)
    
    
    if(SFU_stream$SFU_Stream_Name[r] == "Fannie Left"){
      cond_NUSEDS <- stream_name_PSE$region == region & 
        (stream_name_PSE$WATERBODY == Nuseds_Names |
           stream_name_PSE$CENSUS_SITE == Nuseds_Names |
           stream_name_PSE$sys_nm == Nuseds_Names) 
    }
    
    if(SFU_stream$SFU_Stream_Name[r] == "Rainbow"){
      cond_NUSEDS <- stream_name_PSE$region == region & 
        (stream_name_PSE$WATERBODY == Nuseds_Names |
           stream_name_PSE$CENSUS_SITE == Nuseds_Names |
           stream_name_PSE$sys_nm == Nuseds_Names) &
        grepl(Watershed_Code,stream_name_PSE$WATERSHED_CDE)
    }
    
    nuseds_cut <- unique(stream_name_PSE[cond_NUSEDS,c("region","GFE_ID","WATERBODY","CENSUS_SITE",
                                                    "sys_nm","Y_LAT","X_LONGT","WATERSHED_CDE")])
    
    if(nrow(nuseds_cut) == 1){
      
      SFU_stream$GFE_ID[r] <- nuseds_cut$GFE_ID
      SFU_stream$X_LONGT[r] <- nuseds_cut$X_LONGT
      SFU_stream$Y_LAT[r] <- nuseds_cut$Y_LAT
      SFU_stream$in_PSE[r] <- T
      
    }else{
      print("More than one location matched BREAK")
      print(nuseds_cut)
      break
    }
    
  }else{
    in_PSE <- F
    char <- NA
    
    if(SFU_Stream_Name_simple == "bullocksquare"){
      char <- "bullock"
    }else if(SFU_Stream_Name_simple == "fancyright"){
      char <- "fancy"
    }
    
    if(!is.na(char)){
      
      cond_NUSEDS <- stream_name_PSE$region == region & 
        (grepl(char,simplify_string_fun(stream_name_PSE$WATERBODY)) |
           grepl(char,simplify_string_fun(stream_name_PSE$CENSUS_SITE)) |
           grepl(char,simplify_string_fun(stream_name_PSE$sys_nm))) |
        grepl(Watershed_Code,stream_name_PSE$WATERSHED_CDE)
      
      location_choices <- data.frame(SFU_Stream_Name = SFU_stream$SFU_Stream_Name[r],
                                     GFE_ID = stream_name_PSE$GFE_ID[cond_NUSEDS] |> unique(),
                                     WATERBODY = stream_name_PSE$WATERBODY[cond_NUSEDS] |> unique(),
                                     CENSUS_SITE = stream_name_PSE$CENSUS_SITE[cond_NUSEDS] |> unique(),
                                     sys_nm = stream_name_PSE$sys_nm[cond_NUSEDS] |> unique(),
                                     X_LONGT = stream_name_PSE$X_LONGT[cond_NUSEDS] |> unique(),
                                     Y_LAT = stream_name_PSE$Y_LAT[cond_NUSEDS] |> unique(),
                                     WATERSHED_CDE = stream_name_PSE$WATERSHED_CDE[cond_NUSEDS] |> unique(),
                                     distance = NA,
                                     species_present = NA)
      
      Latitude <- SFU_stream$Latitude[r]
      Longitude <- SFU_stream$Longitude[r]
      
      point <- SpatialPoints(coords = data.frame(x = Longitude, y = Latitude), 
                             proj4string = CRS("+proj=longlat +datum=WGS84"))

      for(rr in 1:nrow(location_choices)){
        # rr <- 1
        point_nuseds <- SpatialPoints(coords = data.frame(x = location_choices$X_LONGT[rr], 
                                                          y = location_choices$Y_LAT[rr]), 
                                      proj4string = CRS("+proj=longlat +datum=WGS84"))
        
        
        location_choices$distance[rr] <- spDists(x = point,y = point_nuseds, longlat = T) |> round(3)
      }
      
      if(nrow(location_maybe) == 0){
        location_maybe <- location_choices
      }else{
        location_maybe <- rbind(location_maybe,location_choices)
      }
      
      in_PSE <- "?"
      
    }else{
      print(paste0("No match based on name - BREAK r = ",r))
      
      show <- data.frame(SFU_Stream_Name = SFU_stream$SFU_Stream_Name[r],
                         Nuseds_Names = SFU_stream$Nuseds_Names[r],
                         Latitude = SFU_stream$Latitude[r],
                         Longitude = SFU_stream$Longitude[r])
      print(show)
      
      # break
    }
    
    SFU_stream$in_PSE[r] <- in_PSE
  }
}
```


There are `r sum(SFU_stream$in_PSE == "TRUE")` locations that matched:

```{r, echo=FALSE}
SFU_stream$WATERBODY <- sapply(SFU_stream$GFE_ID,function(x){
  if(is.na(x)){
    out <- NA
  }else{
    cond <- nuseds_cuid_streamid$GFE_ID == x
    out <- unique(nuseds_cuid_streamid$WATERBODY[cond])
  }
  return(out)
})

cond <- SFU_stream$in_PSE == "TRUE"
SFU_stream[cond,c("region","SFU_Stream_Name","WATERBODY","GFE_ID")]
```

There are `r sum(SFU_stream$in_PSE == "FALSE")` locations that did not match:

```{r, echo=FALSE}
cond <- SFU_stream$in_PSE == "FALSE"
SFU_stream[cond,c("region","SFU_Stream_Name","WATERBODY","GFE_ID")]
```

There are `r sum(SFU_stream$in_PSE == "?")` locations for which we are not sure and we show here the potential matches (`distance` is the distance between SFU's and DFO's locations in km):

```{r, echo=FALSE}
location_maybe[,c("SFU_Stream_Name","GFE_ID","WATERBODY","distance")]
```

To check if any of these location match, we look at the count data. If the counts are the same for several years then it is likely a match (the SFU points are from SFU):

```{r, echo=FALSE, fig.width=10, fig.height=8}
#' There are two locations with potentially multiple match 
#' See if we can find the right location in nuseds looking if the data match
cond <- SFU_stream$in_PSE == "?"
SFU_stream[cond,]
SFU_Stream_Name_check <- SFU_stream$SFU_Stream_Name[cond]

for(sn in SFU_Stream_Name_check){
  # sn <- SFU_Stream_Name_check[1]
  
  cond <- SFU_stream$SFU_Stream_Name == sn
  region <- unique(SFU_stream$region[SFU_stream$SFU_Stream_Name == sn])
  
  cond_sn_sfu <- SFU_escap$reynolds.me == sn
  species <- SFU_escap$species[cond_sn_sfu] |> unique()
  
  if("pink" %in% species){
    species <- species[species != "pink"]
    
    # check if there is data for odd and even years
    cond <- cond_sn_sfu & SFU_escap$species == "pink" & SFU_escap$year %% 2 != 0
    if(any(cond)){
      species <- c(species,"pink odd")
    }
    cond <- cond_sn_sfu & SFU_escap$species == "pink" & SFU_escap$year %% 2 == 0
    if(any(cond)){
      species <- c(species,"pink even")
    }
  }
  
  for(sp in species){
    # sp <- species[1]
    
    cond <- location_maybe$SFU_Stream_Name == sn
    GFE_ID <- location_maybe$GFE_ID[cond]
    CENSUS_SITE <- location_maybe$CENSUS_SITE[cond]
    
    if(sp == "pink odd"){
      cond_sp_sfu <- SFU_escap$species == "pink" & SFU_escap$year %% 2 != 0
      cond_nuseds <- nuseds_cuid_streamid$region == region &
        nuseds_cuid_streamid$SPECIES_QUALIFIED == "PKO" & 
        nuseds_cuid_streamid$GFE_ID %in% GFE_ID
    }else if(sp == "pink even"){
      cond_sp_sfu <- SFU_escap$species == "pink" & SFU_escap$year %% 2 == 0
      cond_nuseds <- nuseds_cuid_streamid$region == region &
        nuseds_cuid_streamid$SPECIES_QUALIFIED == "PKE" & 
        nuseds_cuid_streamid$GFE_ID %in% GFE_ID
    }else{
      cond_sp_sfu <- SFU_escap$species == sp
      cond_nuseds <- nuseds_cuid_streamid$region == region &
        simplify_string_fun(nuseds_cuid_streamid$SPECIES) == sp & 
        nuseds_cuid_streamid$GFE_ID %in% GFE_ID
    }
    
    yr_sfu <- SFU_escap$year[cond_sn_sfu & cond_sp_sfu]
    count_sfu <- SFU_escap$estimate.number[cond_sn_sfu & cond_sp_sfu] |> as.numeric()
    # SFU_escap[cond_sn_sfu,]
    
    if(any(cond_nuseds)){
      
      data <- unique(nuseds_cuid_streamid[cond_nuseds,c("cu_name_pse","IndexId","GFE_ID")])
      
      cu_name_pse <- data$cu_name_pse |> unique()
      
      y_max <- max(max(nuseds_cuid_streamid$MAX_ESTIMATE[cond_nuseds],na.rm = T),
                   max(count_sfu))
      
      plot_IndexId_GFE_ID_fun(IndexIds = data$IndexId, 
                              GFE_IDs = data$GFE_ID, 
                              all_areas_nuseds = nuseds_cuid_streamid, 
                              main = paste0("SFU stream name = ",sn), 
                              Xlim =range(yr_sfu), Ylim = c(0,y_max))
      
      legend("top",CENSUS_SITE,bty = "n")
      legend("bottomleft",paste0("cu_name_pse = ",cu_name_pse),bty = "n")
      
      # plot the SFU data
      lines(x = yr_sfu, y = count_sfu, lty = 5, col = "purple", lwd = 2)
      points(x = yr_sfu, y = count_sfu, lty = 5, col = "purple", lwd = 2, pch = 1, cex = 2)
      
    }else{
      
      plot(x = yr_sfu, y = count_sfu, lty = 5, col = "purple", lwd = 2, 
           type = "l", main = paste0("SFU stream name = ",sn))
      points(x = yr_sfu, y = count_sfu, lty = 5, col = "purple", lwd = 2, pch = 1, cex = 2)
      legend("topleft",sp,bty = "n")
      legend("topright",c("","","NO NUSEDS DATA"),bty = "n")
      legend("topright","SFU",pch = 1, col = "purple",lty = 5,bty = "n",lwd=2,  pt.cex = 2)
    }
  }
}
```

There does not seem to be any match, except may be for **Bullock Square** and **BULLOCK CHANNEL #3 SOUTH CREEK** but the distances between the two are > 4km (as shown in table above), so we decide that these are different locations and time series.


# Merge the two datasets

Here is the procedure:

- if `IndexId/POP_ID` found (so `GFE_ID` found too):

  - if new counts --> add them to NuSEDS
  
  - if counts in conflicts (different value) --> replace values in NuSEDS UNLESS THESE POINTS ARE FROM NUSEDS AS WELL, in which case we keep our data assuming our dataset is more up to date.
  
  - if counts are the same --> do nothing
  
  - in any cases, do not change info about the location
  
- if `IndexId/POP_ID` not found but `GFE_ID` found:
  
  - add time series to NuSEDS 
  
  - do not change info about the location
  
- if `IndexId/POP_ID` not found and `GFE_ID` found:
  
  - add time series to NuSEDS
  
  - add info about the location

Note that it is essential to appropriately update the value of the variables associated to counts, populations and locations. The SFU data is shown with purple circles, those ones with one circle were sourced from NuSEDS (by Reynolds' team), the ones with two circles are Reynolds's own estimates.

```{r}
#' variables to delete the value when editing nuseds_cuid_streamid_Reynolds with 
#' existing IndexId and GFE_ID
var_toDelete <- c("NATURAL_ADULT_SPAWNERS","NATURAL_JACK_SPAWNERS","ADULT_PRESENCE",
                  "JACK_PRESENCE","NATURAL_SPAWNERS_TOTAL","ADULT_BROODSTOCK_REMOVALS",
                  "JACK_BROODSTOCK_REMOVALS","TOTAL_BROODSTOCK_REMOVALS","RUN_TYPE",
                         "OTHER_REMOVALS","TOTAL_RETURN_TO_RIVER","Returns",
                        "START_DTT","END_DTT","NATURAL_ADULT_FEMALES",
                        "NATURAL_ADULT_MALES","EFFECTIVE_FEMALES",
                        "WEIGHTED_PCT_SPAWN","WATERBODY_ID","STREAM_ARRIVAL_DT_FROM",
                        "STREAM_ARRIVAL_DT_TO","START_SPAWN_DT_FROM","START_SPAWN_DT_TO",
                        "PEAK_SPAWN_DT_FROM","PEAK_SPAWN_DT_TO","END_SPAWN_DT_FROM",
                        "END_SPAWN_DT_TO","ACCURACY","PRECISION","INDEX_YN",
                        "RELIABILITY","ESTIMATE_STAGE","NO_INSPECTIONS_USED",
                        "CREATED_DTT","UPDATED_DTT","ACT_ID","Source","Spawners",
                        "SpawnersSource","Broodstock","BroodstockSource","Removals",
                        "RemovalsSource","CMNTS","EFFECTIVE_DT")

#' variables to delete the value when adding rows to nuseds_cuid_streamid_Reynolds
#' with non-existing IndexId and but existing GFE_ID
var_toDelete_IndexId <- c("IndexId","POP_ID","POPULATION","streamid")

#' variables to delete the value when adding rows to nuseds_cuid_streamid_Reynolds
#' with non-existing GFE_ID
var_toDelete_GFE_ID <- c("GFE_ID","WATERSHED_CDE","FWA_WATERSHED_CDE","WATERBODY","sys_nm",               
                         "GAZETTED_NAME","LOCAL_NAME_1","LOCAL_NAME_2","CENSUS_SITE",
                         "X_LONGT","Y_LAT","FAZ_ACRO","MAZ_ACRO","JAZ_ACRO",
                         "AREA","StatArea","IS_INDICATOR","GFE_TYPE","coordinates_changed")
```


```{r, echo=FALSE, fig.width=15, fig.height=8}
#' PROCEDURE
#' if IndexId/POP_ID found (so GFE_ID found too):
#'  - if new counts --> add them to nuseds_cuid_streamid_Reynolds
#'  - if counts in conflicts (different value) --> replace value in nuseds_cuid_streamid_Reynolds 
#'    from SFU_escap UNLESS THESE POINTS ARE FROM NUSEDS AS WELL, in which case we 
#'    keep our data assuming our dataset is more up to date. 
#'  - if counts are the same --> do nothing and keep source_id = "NuSEDS_20251103"
#'  - do not change info about the location
#' if IndexId/POP_ID not found but GFE_ID found:
#'  - do not change info about the location
#'  - add time series to nuseds_cuid_streamid_Reynolds 
#' if IndexId/POP_ID not found and GFE_ID found:
#'  - add info about the location
#'  - add time series to nuseds_cuid_streamid_Reynolds

nuseds_cuid_streamid_Reynolds <- nuseds_cuid_streamid

count <- 0
for(r in 1:nrow(SFU_stream)){
  # r <- 1
  # r <- which(is.na(SFU_stream$GFE_ID))[1]
  # r <- which(SFU_stream$SFU_Stream_Name == "Bullock Square")[1]
  
  SFU_Stream_Name <- SFU_stream$SFU_Stream_Name[r]
  Nuseds_Names <- SFU_stream$Nuseds_Names[r]
  GFE_ID <- SFU_stream$GFE_ID[r]
  region <- SFU_stream$region[r]
  
  # get the species in SFU dataset
  cond_sn_sfu <- SFU_escap$reynolds.me == SFU_Stream_Name
  species <- SFU_escap$species[cond_sn_sfu] |> unique()
  
  if("pink" %in% species){
    species <- species[species != "pink"]
    
    # check if there is data for odd and even years
    cond <- cond_sn_sfu & SFU_escap$species == "pink" & SFU_escap$year %% 2 != 0
    if(any(cond)){
      species <- c(species,"pink odd")
    }
    cond <- cond_sn_sfu & SFU_escap$species == "pink" & SFU_escap$year %% 2 == 0
    if(any(cond)){
      species <- c(species,"pink even")
    }
  }

  for(sp in species){
    # sp <- species[4]
    
    if(sp == "pink odd"){
      cond_sp_sfu <- SFU_escap$species == "pink" & SFU_escap$year %% 2 != 0
    }else if(sp == "pink even"){
      cond_sp_sfu <- SFU_escap$species == "pink" & SFU_escap$year %% 2 == 0
    }else{
      cond_sp_sfu <- SFU_escap$species == sp
    }
    
    # Get the SFU counts
    yr_sfu <- SFU_escap$year[cond_sn_sfu & cond_sp_sfu]
    count_sfu <- SFU_escap$estimate.number[cond_sn_sfu & cond_sp_sfu] |> as.numeric()
    # SFU_escap[cond_sn_sfu,]
    
    layout(matrix(1))
    
    cond_nuseds <- F
    if(!is.na(GFE_ID)){
      
      if(sp == "pink odd"){
        cond_nuseds <- nuseds_cuid_streamid$region == region &
          nuseds_cuid_streamid$SPECIES_QUALIFIED == "PKO" & 
          nuseds_cuid_streamid$GFE_ID %in% GFE_ID
      }else if(sp == "pink even"){
        cond_nuseds <- nuseds_cuid_streamid$region == region &
          nuseds_cuid_streamid$SPECIES_QUALIFIED == "PKE" & 
          nuseds_cuid_streamid$GFE_ID %in% GFE_ID
      }else{
        cond_nuseds <- nuseds_cuid_streamid$region == region &
          simplify_string_fun(nuseds_cuid_streamid$SPECIES) == sp & 
          nuseds_cuid_streamid$GFE_ID %in% GFE_ID
      }
    }
    
    if(any(cond_nuseds)){
      
      data <- unique(nuseds_cuid_streamid[cond_nuseds,c("cu_name_pse","IndexId",
                                                        "GFE_ID","cuid","CENSUS_SITE")])
      cu_name_pse <- data$cu_name_pse |> unique()
      cuid <- data$cuid |> unique()
      CENSUS_SITE <- data$CENSUS_SITE |> unique()
      
      yr_nuseds <- nuseds_cuid_streamid$Year[cond_nuseds]
      count_nuseds <- nuseds_cuid_streamid$MAX_ESTIMATE[cond_nuseds]
      yr_nuseds <- yr_nuseds[!is.na(count_nuseds)]
      
      plot_IndexId_GFE_ID_fun(IndexIds = data$IndexId, 
                              GFE_IDs = data$GFE_ID, 
                              all_areas_nuseds = nuseds_cuid_streamid, 
                              main = paste0(cu_name_pse," (CUID = ",cuid,")"), 
                              pchs = 16, 
                              Ylim = c(0,max(max(count_nuseds,na.rm = T),max(count_sfu,na.rm = T))),
                              Xlim = c(min(c(min(yr_nuseds),min(yr_sfu))),
                                       max(c(max(yr_nuseds, na.rm = T),max(yr_sfu)))))
      
      legend("top",CENSUS_SITE,bty = "n")
      
      # plot the SFU data
      # lines(x = yr_sfu, y = count_sfu, lty = 5, col = "purple", lwd = 2)
      points(x = yr_sfu, y = count_sfu, lty = 5, col = "purple", lwd = 2, pch = 1, cex = 2)
      
      count <- count + 1
      legend("bottomleft",paste0("n = ",count), bty = "n")
      
      # show the points that are not NUSEDS but SFU
      cond_sfu <- SFU_escap$estimate.source == "SFU"
      yr_sfu_sfu <- SFU_escap$year[cond_sn_sfu & cond_sp_sfu & cond_sfu]
      count_sfu_sfu <- SFU_escap$estimate.number[cond_sn_sfu & cond_sp_sfu & cond_sfu] |> as.numeric()
      points(x = yr_sfu_sfu, y = count_sfu_sfu, lty = 5, col = "purple", lwd = 2, pch = 1, cex = 3)
      
      # Edit Nuseds
      nuseds_here <- nuseds_cuid_streamid[cond_nuseds,]
      nuseds_here <- nuseds_here[order(nuseds_here$Year),]
      SFU_escap_here <- SFU_escap[cond_sn_sfu & cond_sp_sfu,]
      SFU_escap_here <- SFU_escap_here[order(SFU_escap_here$year),]
      
      # Replace in nuseds_cuid_streamid_Reynolds the raw with conflicting data points
      # 1st: find years in common
      cond_common <- nuseds_here$Year %in% SFU_escap_here$year
      
      # 2nd: find rows in conflicts
      cond_conflict <- rep(F,nrow(nuseds_here))
      for(i in 1:nrow(nuseds_here)){
        cond_yr <- SFU_escap_here$year == nuseds_here$Year[i]
        if(any(cond_yr)){
          cond_true <- is.na(nuseds_here$MAX_ESTIMATE[i]) |
            (!is.na(nuseds_here$MAX_ESTIMATE[i]) & nuseds_here$MAX_ESTIMATE[i] != SFU_escap_here$estimate.number[cond_yr])
          if(cond_true){
            cond_conflict[i] <- T
          }
        }
      }
      
      # 3rd : edit the row in conflict
      if(any(cond_conflict)){
        
        data_merge <- merge(x = SFU_escap_here,
                            y = nuseds_here[cond_conflict,c("Year","MAX_ESTIMATE","IndexId","GFE_ID")],
                            by.x = "year",by.y = "Year")
        
        # check if any of those conflictual points are in SFU - NUSEDS
        cond <- data_merge$estimate.source == "NuSEDS"
        if(any(cond)){
          print("Certain conflictual points in SFU datasets are from NuSEDS --> we do not take these data.")
          print(data_merge[cond,])
          print("***")
          data_merge <- data_merge[!cond,]
        }
        
        if(nrow(data_merge) > 0){
          
          IndexId <- unique(data_merge$IndexId) # should be unique
          GFE_ID <- unique(data_merge$GFE_ID)   # should be unique
          
          for(i in 1:nrow(data_merge)){
            
            cond <- !is.na(nuseds_cuid_streamid_Reynolds$IndexId) &
              nuseds_cuid_streamid_Reynolds$IndexId == IndexId & 
              !is.na(nuseds_cuid_streamid_Reynolds$GFE_ID) &
              nuseds_cuid_streamid_Reynolds$GFE_ID == GFE_ID &
              nuseds_cuid_streamid_Reynolds$Year == data_merge$year[i]

            nuseds_cuid_streamid_Reynolds$MAX_ESTIMATE[cond] <- data_merge$estimate.number[i]
            nuseds_cuid_streamid_Reynolds$ESTIMATE_METHOD[cond] <- data_merge$estimate.method[i]
            nuseds_cuid_streamid_Reynolds$ESTIMATE_CLASSIFICATION[cond] <- data_merge$ESTIMATE_CLASSIFICATION[i]
            nuseds_cuid_streamid_Reynolds$stream_survey_quality[cond] <- data_merge$stream_survey_quality[i]
            nuseds_cuid_streamid_Reynolds$source_id[cond] <- data_merge$source_id[i]
            nuseds_cuid_streamid_Reynolds$ENUMERATION_METHODS[cond] <- ""
          }
          
          # set the values for fields associated to measurement to NA
          cond <- !is.na(nuseds_cuid_streamid_Reynolds$IndexId) &
            nuseds_cuid_streamid_Reynolds$IndexId == IndexId & 
            !is.na(nuseds_cuid_streamid_Reynolds$GFE_ID) &
            nuseds_cuid_streamid_Reynolds$GFE_ID == GFE_ID &
            nuseds_cuid_streamid_Reynolds$Year %in% data_merge$year
          
          for(c in var_toDelete){
            nuseds_cuid_streamid_Reynolds[cond,c] <- NA
          }
        }
      }
      
      # 4th: find the years with data not in nuseds_cuid_streamid_Reynolds
      cond_add <- ! SFU_escap_here$year %in% nuseds_here$Year
      if(any(cond_add)){
        
        SFU_escap_here_add <- SFU_escap_here[cond_add,,drop = F]
        
        # check if any of those extra points are in SFU - NUSEDS
        cond <- SFU_escap_here_add$estimate.source == "NuSEDS"
        if(any(cond)){
          print("Certain additional points in SFU datasets are from NuSEDS --> we do not take these data.")
          print(SFU_escap_here_add[cond,])
          print("***")
          SFU_escap_here_add <- SFU_escap_here_add[!cond,]
        }
        
        if(nrow(SFU_escap_here_add) > 0){
          
          nuseds_add <- create_empty_dataset_fun(dataset = nuseds_cuid_streamid[cond_nuseds,],
                                                 n_row = nrow(SFU_escap_here_add),
                                                 col_toChange = c(var_toDelete)) #
          
          nuseds_add$Year <- SFU_escap_here_add$year
          nuseds_add$MAX_ESTIMATE <- SFU_escap_here_add$estimate.number
          nuseds_add$ESTIMATE_METHOD <- SFU_escap_here_add$estimate.method
          nuseds_add$ESTIMATE_CLASSIFICATION <- SFU_escap_here_add$ESTIMATE_CLASSIFICATION
          nuseds_add$stream_survey_quality <- SFU_escap_here_add$stream_survey_quality
          nuseds_add$source_id <- SFU_escap_here_add$source_id
          
          # set the values associate to count to NA
          for(c in var_toDelete){
            nuseds_add[,c] <- NA
          }
          
          # add the data to nuseds_cuid_streamid_Reynolds
          nuseds_cuid_streamid_Reynolds <- rbind(nuseds_cuid_streamid_Reynolds,nuseds_add)
        }
      }
      
      # plot updated nuseds data
      plot_IndexId_GFE_ID_fun(IndexIds = data$IndexId, 
                              GFE_IDs = data$GFE_ID, 
                              all_areas_nuseds = nuseds_cuid_streamid_Reynolds, 
                              main = paste0(cu_name_pse," (CUID = ",cuid,")"), 
                              pchs = 16,                              
                              Ylim = c(0,max(max(count_nuseds,na.rm = T),max(count_sfu,na.rm = T))),
                              Xlim = c(min(c(min(yr_nuseds),min(yr_sfu))),
                                       max(c(max(yr_nuseds, na.rm = T),max(yr_sfu)))))
      legend("top",CENSUS_SITE,bty = "n")
      points(x = yr_sfu, y = count_sfu, lty = 5, col = "purple", lwd = 2, pch = 1, cex = 2)
      legend("bottomleft",paste0("n = ",count), bty = "n")
      legend("topright","AFTER", bty = "n")
      
    }else{ #'* The time series is not in NuSEDS * 
      
      if(is.na(GFE_ID)){
        print(paste("Location",SFU_Stream_Name,"is not in NuSEDS"))
      }else{
        print(paste("The population of species",sp,"at location",SFU_Stream_Name,"is not in NuSEDS (location is in NuSEDS)"))
      }
      
      point <- st_as_sf(SFU_stream[r,], 
                        coords = c("Longitude","Latitude"), crs = 4269)
      
      if(sp == "pink odd"){
        cond_cu_layer <- CUs_gdb$region_name == region & 
          CUs_gdb$species_qualified == "Pink odd"
      }else if(sp == "pink even"){
        cond_cu_layer <- CUs_gdb$region_name == region & 
          CUs_gdb$species_qualified == "Pink even"
      }else{
        cond_cu_layer <- CUs_gdb$region_name == region & 
          simplify_string_fun(CUs_gdb$species_name) == sp
      }
      
      layer_CU <- st_intersects(point,CUs_gdb[cond_cu_layer,])
      
      # plot(st_geometry(regions_shp[regions_shp$Region == region,]))
      # plot(st_geometry(CUs_gdb[cond_cu_layer,]),col = rainbow(n = sum(cond_cu_layer), alpha = .3), add = T)
      # plot(st_geometry(CUs_gdb[cond_cu_layer,][layer_CU[[1]],]),
      #      col = rainbow(n = length(layer_CU[[1]]), alpha = .3), add = T)
      # plot(st_geometry(point), add = T, col = "red", pch = 16, cex = 2)
      
      if(length(layer_CU[[1]]) == 0){ # buffer
        layer_CU <- st_intersects(point, st_buffer(CUs_gdb[cond_cu_layer,],dist = .05))
      }
      
      if(sp == "sockeye" & SFU_Stream_Name == "Ada"){
        # there are two choices
        # Northern Coastal Streams         SER-17     SER Current  615
        # Fannie Cove                   SEL-19-10     SEL Current  549 --> the one I believe
        i <- which(CUs_gdb[cond_cu_layer,][layer_CU[[1]],]$cu_name_pse == "Fannie Cove")
        layer_CU <- list(layer_CU[[1]][i])
      }
      
      if(length(layer_CU[[1]]) != 1){ # 
        print(paste("Problem finding layer - ",SFU_Stream_Name," - ",sp))
        
      }else{
        
        cu_name_pse <- CUs_gdb[cond_cu_layer,][layer_CU[[1]],]$cu_name_pse
        cuid <- CUs_gdb[cond_cu_layer,][layer_CU[[1]],]$CUID
        
        plot(x = yr_sfu, y = count_sfu, lty = 5, col = "purple", lwd = 2, 
             type = "l", main = paste0(cu_name_pse," (CUID = ",cuid,") INTERSECTED"),
             xlab= "Year", ylab = "MAX_ESTIMATE")
        points(x = yr_sfu, y = count_sfu, lty = 5, col = "purple", lwd = 2, pch = 1, cex = 2)
        legend("topleft",sp,bty = "n")
        if(is.na(GFE_ID)){
          legend("topright","LOCATION NOT IN NUSEDS",bty = "n")
        }else{
          legend("topright","POPULATION NOT IN NUSEDS (location is)",bty = "n")
        }
        
        count <- count + 1
        legend("bottomleft",paste0("n = ",count), bty = "n")
        
        # Add the data to nuseds_cuid_streamid_Reynolds
        SFU_escap_here_add <- SFU_escap[cond_sn_sfu & cond_sp_sfu,,drop = F]
        SFU_escap_here_add <- SFU_escap_here_add[order(SFU_escap_here_add$year),]
        
        # check if any of those extra points are in SFU - NUSEDS --> should not be
        cond <- SFU_escap_here_add$estimate.source == "NuSEDS"
        if(any(cond)){
          print("This time series is not in our cleaned NuSEDS but it is sourced from NuSEDS in SFU data --> CHECK")
          print(SFU_escap_here_add[cond,])
          print("***")
        }
        
        if(is.na(GFE_ID)){
          
          # get the info of the CU
          cond_nuseds <- !is.na(nuseds_cuid_streamid$cuid) &
            nuseds_cuid_streamid$cuid == cuid
          
          nuseds_add <- create_empty_dataset_fun(dataset = nuseds_cuid_streamid[cond_nuseds,],
                                                 n_row = nrow(SFU_escap_here_add),
                                                 col_toChange = c(var_toDelete,
                                                                  var_toDelete_IndexId,
                                                                  var_toDelete_GFE_ID)) # set all the location-related fields to NA
          
          # add the values for the fields related to location
          nuseds_add$sys_nm <- SFU_escap_here_add$reynolds.me
          # nuseds_add$WATERBODY <- SFU_escap_here_add$reynolds.me
          # nuseds_add$CENSUS_SITE <- SFU_escap_here_add$reynolds.me
          
          # find the coordinates
          cond <- SFU_stream$SFU_Stream_Name == unique(SFU_escap_here_add$reynolds.me)
          nuseds_add$X_LONGT <- SFU_stream$Longitude[cond]
          nuseds_add$Y_LAT <- SFU_stream$Latitude[cond]
          nuseds_add$WATERSHED_CDE <- SFU_stream$Watershed_Code[cond]
          
          legend("top",nuseds_add$sys_nm[1],bty = "n")
          
        }else{ # if GFE_ID is not NA --> we keep the info related to locations
          
          # we cannot get the cuid and GFE_ID location at the same time because
          # the combination of the two does not exist in NuSEDS yet
          
          # get the cuid-related info
          cond_nuseds <-  !is.na(nuseds_cuid_streamid$cuid) & 
            nuseds_cuid_streamid$cuid == cuid
          
          nuseds_add <- create_empty_dataset_fun(dataset = nuseds_cuid_streamid[cond_nuseds,],
                                                 n_row = nrow(SFU_escap_here_add),
                                                 col_toChange = c(var_toDelete,
                                                                  var_toDelete_IndexId,
                                                                  var_toDelete_GFE_ID)) # set all the location-related fields to NA for now
          
          # get the GFE_ID-related info
          cond_nuseds <- nuseds_cuid_streamid$GFE_ID == GFE_ID
          
          nuseds_add_gfeid <- create_empty_dataset_fun(dataset = nuseds_cuid_streamid[cond_nuseds,],
                                                       n_row = 1,
                                                       col_toChange = c(var_toDelete,
                                                                        var_toDelete_IndexId))
          # edit nuseds_add 
          for(c in var_toDelete_GFE_ID){
            nuseds_add[,c] <- nuseds_add_gfeid[,c]
          }
          
          legend("top",nuseds_add$CENSUS_SITE[1],bty = "n")
        }
        
        # edit the rest of the fields
        nuseds_add$Year <- SFU_escap_here_add$year
        nuseds_add$MAX_ESTIMATE <- SFU_escap_here_add$estimate.number
        nuseds_add$ESTIMATE_METHOD <- SFU_escap_here_add$estimate.method
        nuseds_add$ESTIMATE_CLASSIFICATION <- SFU_escap_here_add$ESTIMATE_CLASSIFICATION
        nuseds_add$stream_survey_quality <- SFU_escap_here_add$stream_survey_quality
        nuseds_add$source_id <- SFU_escap_here_add$source_id
        
        # add the data to nuseds_cuid_streamid_Reynolds
        nuseds_cuid_streamid_Reynolds <- rbind(nuseds_cuid_streamid_Reynolds,nuseds_add)
        
        # plot updated nuseds data
        cond <- !is.na(nuseds_cuid_streamid_Reynolds$cuid) & 
          nuseds_cuid_streamid_Reynolds$cuid == cuid &
          nuseds_cuid_streamid_Reynolds$sys_nm == unique(nuseds_add$sys_nm)
        
        data <- nuseds_cuid_streamid_Reynolds[cond,]
        data <- data[order(data$Year),]
        
        plot(x = data$Year, y = data$MAX_ESTIMATE, lty = 1, col = "red", lwd = 2, 
             type = "l", main = paste0(cu_name_pse," (CUID = ",cuid,") INTERSECTED"),
             xlab= "Year", ylab = "MAX_ESTIMATE")
        points(x = data$Year, y = data$MAX_ESTIMATE, col = "red", cex = 1, pch = 16)
                if(is.na(GFE_ID)){
          legend("top",data$sys_nm[1],bty = "n")
        }else{
          legend("top",data$WATERBODY[1],bty = "n")
        }
        points(x = yr_sfu, y = count_sfu, lty = 5, col = "purple", lwd = 2, pch = 1, cex = 2)
        legend("bottomleft",paste0("n = ",count), bty = "n")
        legend("topright","AFTER", bty = "n")
      }
    }
  }
}
```

# Export dataset

```{r}
if(export_datasets){
  date <- Sys.Date()
  write.csv(nuseds_cuid_streamid_Reynolds,
            paste0(wd_output,"/archive/3_nuseds_cuid_streamid_Reynolds_",date,".csv"),
            row.names = F)
}
```










